% !TEX program = xelatex

\documentclass{resume}
\usepackage{hyperref}
\usepackage[UTF8]{ctex}
\usepackage{setspace}

\setstretch{0.88}
\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{YaoYang Ye}

\basicInfo{
  \email{makise@zju.edu.cn} \textperiodcentered\ 
  \github[github.com/CubicYYY]{https://github.com/CubicYYY} \textperiodcentered\ 
  \homepage[self.cubicy.icu]{https://self.cubicy.icu} \textperiodcentered\ 
}
\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{Zhejiang University (ZJU)}}{Hangzhou, Zhejiang, China}
\datedline{B.Eng. in Computer Science and Technology}{2021.9 -- 2025.6(scheduled)}
\begin{itemize}
  \item Expected Graduation: \textbf{2025.6}
  \item Grades of Recent 2 Years: \textbf{91.45/100}
  \item Overall GPA: \textbf{3.91/4.0 (89.41/100)}
\end{itemize}

\datedsubsection{\textbf{The University of Tokyo}}{Tokyo, Japan}
\datedline{Exchange Student in the USTEP Program}{2024.10 -- 2025.3(scheduled)}

\section{\faLightbulbO\ Research Interests}
\subsection{\textbf{Program Analysis}}
Developing faster, easy-to-use techniques to discover defects automatically, especially for modern programming languages.

\subsection{\textbf{Formal Verification}}
Applying scalable formal methods to prove the security of programs, particularly in concurrent environments, or under side-channel attacks.

\subsection{\textbf{Type System}}
Reducing the mental burden for developers to create parallelizable, scalable, and safe applications.

\subsection{\textbf{Web Security}}
Automated and scalable approaches for identifying vulnerabilities and their exploitation in real-world scenarios.

\section{\faSearch\ Research Experiences}
\datedsubsection{\textbf{Synthesis for Resistance to Side-Channel Attacks}}{2024.9 - Present}  
Supervised by Prof. Jingbo Wang, Purdue University.  
\begin{itemize}  
  \item Investigating automated masking techniques to ensure sensitive data bits are appropriately protected.  
  \item Exploring automated program rewriting methods to prevent leakage of secrets through differential analysis of circuit delay.
\end{itemize}

\datedsubsection{\textbf{Pointer Analysis Acceleration}}{2024.2 - Present}  
Supervised by Prof. Peisen Yao, Zhejiang University.  
\begin{itemize}  
  \item Optimizing set operations in pointer analysis by designing efficient data structures.  
  \item Iteratively analyzed the impact of various LLVM optimization passes on pointer analysis performance.  
  \item Developed a guideline for selecting optimal combinations of LLVM optimization passes for different programs.  
\end{itemize}

\section{\faUsers\ Internships}
\datedsubsection{\textbf{Shanghai Luogu Network Technology Co., Ltd} Shanghai, China}{2021 -- 2023}
\role{Backend Development / Lecturer}{~}
The most famous online judger for competitive programming in China.

\section{\faBook\ Teaching}
\datedsubsection{\textbf{CTF101: Attack and Defence Practice Course} in Zhejiang University}{2023, 2024}
\role{Lecturer / Teaching Assistant}{Misc / Web courses}

\section{\faCode\ Projects}
\datedsubsection{\textbf{Website for People of the Chinese Imperial Examinations}}{2023 -- 2024}
\role{Technical Leader}{Fullstack Developer / DevOps}
A digitization project featuring a large database and an modern interactive web interface.\\
Collaborated with the College of History.

\datedsubsection{\textbf{RIoT}}{2024}
\role{Course project}{Rust, Vue.js}
A high-performance IoT platform built on Actix Web.

\datedsubsection{\textbf{Vodis}}{2023}
\role{Course project}{Rust}
A Redis-like in-memory database, based on Volo-Thrift RPC framework by ByteDance.

\section{\faBookmarkO\ Publications}
Currently work in progress.

\section{\faCogs\ Skills}
\subsection{\textbf{Programming}}
\begin{itemize}[parsep=0.5ex]
  \item >10k lines: C++ > Rust > Python
  \item 5k-10k lines: JavaScript(Node.js) > PHP > MATLAB
  \item <5k lines: Java > Vue.js > React.js > Haskell
\end{itemize}
\subsection{\textbf{Language}}
\begin{itemize}[parsep=0.5ex]
  \item Mandarin: native speaker
  \item English: fluent, TOEFL 100 (R27 L26 S23 W24) (first attempt)
  \item Japanese: capable of daily communications
\end{itemize}

\section{\faHeartO\ Honors and Awards}
\datedline{\textit{\nth{2} Class Prize} University Scholarships for Excellent Student, Zhejiang University}{2023}
\datedline{\textit{\nth{2} Place}, SECCON 2023, Tokyo, Japan (team AAA)}{2023.12}
\datedline{\textit{\nth{2} Place}, CODEGATE 2023, Seoul, Korea (team AAA)}{2023.8}
\datedline{\textit{\nth{3} Class Prize} University Scholarships for Excellent Student, Zhejiang University}{2022}
\datedline{\textit{\nth{1} Place(Mainland China)}, \textit{\nth{9} Place(Global)}, TCTF RisingStar 2022 Quals (team AAA)}{2022.9}
\datedline{\textit{\nth{3} Place}, ByteCTF 2021 (team AAA)}{2021.12}
\datedline{\textit{\nth{1} Class Prize}, National Olympiad in Informatics(Fujian Province)}{2018}

\section{\faInfo\ Extracurricular Activities}
\datedsubsection{\textbf{ZJU Azure Assassin Alliance CTF Team}}{2021 -- Present}
\role{Member}{Specialized in Web and Misc challenges.}

\datedsubsection{\textbf{ZJU X-Lab}}{2022 -- Present}
\role{Full Stack Developer}{Primarily working with Rust, Next.js, and Python.}

\section{\faInfo\ Miscellaneous}
\begin{description}[parsep=0.5ex]
  \item[Personal Blog] \url{https://cubicy.icu}
  \item[Math Courses] Took basic courses in abstract algebra and category theory.
\end{description}

\end{document}